Deep learning models for identifying crop and field attributes from near surface cameras

### 2021-10-18 manuscript/main.tex
abstract and conclusion

%%%%%% Abstract %%%%%%
\begin{abstract}

\end{abstract}

@@

Monitoring and assessing crop extent and status using a consistent, data-driven approach is essential to meeting the growing demand for food while meeting our sustainability goals in light of climate change. We formulated a workflow using deep learning methods applied to PhenoCam time series to generate a daily crop phenology time series for locations across the continental U.S. The method can be adapted for other time series or sites, offers a probability distribution for assigned image classes, and integrates an HMM model that accounts for correlation across time. The models and outputs offer a way to calibrate and refine existing models for mapping crop status and yield using satellite remote sensing.

>>>>

%%%%%% Abstract %%%%%%
\begin{abstract}
Near surface cameras, such as those in the PhenoCam network, are a common source of ground truth data in modelling and remote sensing studies. Despite having locations across numerous agricultural sites, few studies have used near surface cameras to track the unique phenology of croplands. Due to management, crops do not have a natural vegetation cycle which many phenological extraction methods are based on. For example, a field may experience abrupt changes due to harvesting and tillage throughout the year. A single camera can also record several different plants due to crop rotations, fallow fields, and cover crops. Current methods to estimate phenology metrics from image time series compress all image information into a relative greenness metric, which discards a large amount of contextual information. This can include the type of crop present, whether snow or water is present on the field, the crop phenology, or whether a field lacking green plants consists of bare soil, fully senesced plants, or plant residue. 
Here we developed a modelling workflow to create a daily time series of crop type and phenology.  while also accounting for other factors such as obstructed images and snow covered fields. We used a mainstream deep learning image classification model, VGG16. Deep learning classification models do not have a temporal component, so to account for temporal correlation of the images our workflow incorporates a hidden markov model in the post-processing. The initial image classification model had out of sample F1 scores of 0.83-0.85, which improved to 0.86-0.91 after all post-processing steps. The resulting time series show the progression of crops from emergence to harvest, and can serve as a daily, local scale dataset of field states and phenological stages for agricultural research.
\end{abstract}

@@

Monitoring and assessing crop extent and status using a consistent, data-driven approach is essential to meeting the growing demand for food while meeting our sustainability goals in light of climate change. We formulated a workflow using a deep learning model applied to PhenoCam time series to generate a daily crop phenology time series for locations across the continental U.S. The workflow uses an HMM to account for the temporal correlation of daily images. The resulting outputs offer a ground truth to calibrate and refine existing models for mapping crop status and yield using satellite remote sensing.
